Changelog

### 2021-05-25 Chapter-6/Chapter-6.tex
Updates from Overleaf

\chapter{Discussion and Limitations}
\section{Fast and Precise Side-channel Vulnerability Detection}
\textbf{Coverage.} \detect{} works on native x86 execution traces. The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also share the common limitations of dynamic approaches. \detect{} may only cover part of the code. Each time we only get one single execution trace. Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed. However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs. Our evaluation also confirms the above intuition. For symmetric encryption, there is no secret-dependent control-flow transfers during our evaluation. RSA implementations have several secret-dependent control-flow transfers. Many of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.

\textbf{Design Choices.} At the early stage of the project, we use SMT solvers to get the solutions of constraints. However, we find for some ciphers (RSA), \detect{} times out after several days. The profiling result shows that it is spending most its time in Z3. Later, we use a sampling method to detect side-channel leakages. The sampling method seems simple and may miss some leakages in theory. However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

\textbf{Cache Model.} We use a simple cache model in this work. Recent work~\cite{Brotzman19Casym,182946} uses an LRU cache. First, there is no fundamental difficulties for us to adopt a more realistic cache models. Second, the LRU model is still a substantial simplification of a real cache. However, the choice of a logical model of cache can bring expensive overheads.

\textbf{Leakages.} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages. 
\section{Precise Analysis on Single-trace Attacks}
While recent work found many side-channel vulnerabilities,
we note that many of them have not been patched by developers.
Side-channels are ubiquitous in software and it would be difficult to fix all of them.
We need a tool that estimates the sensitivity of each vulnerability
so software engineers can focus on
``severe'' leakages. For example, \tool{} reports that
the modular exponentiation using square and multiply algorithms can
leak more information than a key validation function.

>>>>

\chapter{Discussion and Limitations}
\section{Fast and Precise Side-channel Vulnerability Detection}
\subsection*{Coverage} \detect{} works on native x86 execution traces. The design, which is very precise in terms of true leakages compared to other static source code method~\cite{197207,BacelarAlmeida:2013:FVS:2483313.2483334}, also share the common limitations of dynamic approaches. \detect{} may only cover part of the code. Each time we only get one single execution trace. Therefore, we may neglect some side-channel vulnerabilities not covered by the traces analyzed. However, this is not a crucial problem for analyzing cryptographic libraries, because cryptographic libraries are designed to have the same code coverage for various inputs. Our evaluation also confirms the above intuition. For symmetric encryption, there is no secret-dependent control-flow transfers during our evaluation. RSA implementations have several secret-dependent control-flow transfers. Many of them are bound checks, which do not leak much information and have negligible effects on the whole code coverage as well.

\subsection*{Design Choices.} At the early stage of the project, we use SMT solvers to get the solutions of constraints. However, we find for some ciphers (RSA), \detect{} times out after several days. The profiling result shows that it is spending most its time in Z3. Later, we use a sampling method to detect side-channel leakages. The sampling method seems simple and may miss some leakages in theory. However, the evaluation result shows \detect{} can identify all leakages found by the previous work~\cite{203878,236338,Brotzman19Casym}.

\subsection*{Cache Model} We use a simple cache model in this work. Recent work~\cite{Brotzman19Casym,182946} uses an LRU cache. First, there is no fundamental difficulties for us to adopt a more realistic cache models. Second, the LRU model is still a substantial simplification of a real cache. However, the choice of a logical model of cache can bring expensive overheads.

\subsection*{Leakages.} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. The DES implementation of OpenSSL has several sensitive leakages, but given the end life status of DES, it is still unpatched for the worth of engineering effort. After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which partially explain why developers are not interested in fix all the leakages. 
\section{Precise Analysis on Single-trace Attacks}
While recent work found many side-channel vulnerabilities,
we note that many of them have not been patched by developers.
Side-channels are ubiquitous in software and it would be difficult to fix all of them.
We need a tool that estimates the sensitivity of each vulnerability
so software engineers can focus on
``severe'' leakages. For example, \tool{} reports that
the modular exponentiation using square and multiply algorithms can
leak more information than a key validation function.

### 2021-05-25 changelog.tex
Updates from Overleaf

It is possible to extend the quantification part to include other side-channel signals. The key is to model the noises (e.g., Sound, CPU usages, EM signals) properly. In my dissertation, we assume that an attacker can have a noise-free observation. While a noise-free observation is possible for some address-based side-channel attacks, the assumption is too ideal for many other side-channel attacks. The good news is that there are some mature methods in information theory to model the noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a computable method to estimate the information that can be reliably transferred over a channel between secret data and attackers' observations. From a research project aspect, I hope to have a stronger motivation before starting the project. 
\item \textbf{A bits vs. Q bits. Lower bounds?
       Improve the presentation
       Make the comparison more meaningful
       Etc.}

@@

The situation is a little different for a deep learning model. In the dissertation, we evaluated Quincunx on a deep learning model. Each time, we randomly select an item from a dataset (Samples). If the dataset is biased, then we can not get the correct results. The good news is that the most well-known data in machine learning is i.i.d. i.i.d. is the foundation of supervised machine learning algorithms. In my dissertation, we used MINIST, a well-known handwriting dataset. We believe the dataset is i.i.d.

>>>>

It is possible to extend the quantification part to include other side-channel signals (e.g., Sound, CPU usages, EM signals). The key is to model the noises properly. In my dissertation, we assume that an attacker can have a noise-free observation. While a noise-free observation is possible for some address-based side-channel attacks, the assumption is too ideal for many other side-channel attacks. The good news is that there are some mature methods in information theory to model the noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a computable method to estimate the information that can be reliably transferred over a channel between secret data and attackers' observations. From a research project aspect, I hope to have a stronger motivation before starting the project. 
\item \textbf{A bits vs. Q bits. Lower bounds?
       Improve the presentation
       Make the comparison more meaningful
       Etc.}

@@

The situation is a little different for a machine learning library. In the dissertation, we evaluated Quincunx on a deep learning model. Each time, we randomly select an item from a dataset (Samples). If the dataset is biased, then we can not get correct results. The good news is that the most well-known data in machine learning is i.i.d. i.i.d. is the foundation of supervised machine learning algorithms. In my dissertation, we used MINIST, a well-known handwriting dataset. We believe the dataset is i.i.d.
